# Install the required packages
```{r}
library("ggplot2")
library("dplyr")
library("quantmod")
library("rvest")
library("readr")
library("stringr")
library("tidyverse")
library("reticulate")
```

# Set the working directory to the project root
```{r}
project_dir <- this.path::here()
setwd(project_dir)
# Use the virtual environment created with Python 3.12 and PyTorch
use_virtualenv(file.path(project_dir, ".venv"), required = TRUE)
py_config()
getwd()
```

# Get all tickers from the S&P 500 index
```{r}
tickers <- read_html(
  "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
) |>
  html_table() |>
  _[[1]] |>
  select(Symbol) |>
  pull()
head(tickers)
```

# Get the stock data from Yahoo Finance for all the tickers and save it to a cache folder
```{r, results='hide', message=FALSE}
pb <- txtProgressBar(min = 0, max = length(tickers), style = 3)
for (ticker in tickers) {
  setTxtProgressBar(pb, which(ticker == tickers))
  # Replace dots with dashes for Yahoo Finance compatibility
  ticker <- str_replace_all(ticker, "\\.", "-")
  tryCatch({
    dir.create("cache", showWarnings = FALSE)
    if (file.exists(paste0("cache/", ticker, ".csv"))) {
      next
    }
    df <- loadSymbols(
                      Symbols = ticker,
                      from = "2020-01-01",
                      to = "2026-03-31",
                      auto.assign = FALSE) |>
      as.data.frame() |>
      rownames_to_column(var = "Date") |>
      select(Date, ends_with("Close"))
    write_csv(df, paste0("cache/", ticker, ".csv"))
  }, error = function(e) {
    message(
      paste("Error occurred while loading data for", ticker, ": ", e$message)
    )
  })
}
close(pb)
```

# Combine all the close prices into a single data frame for train set from 2020-01-01 to 2025-12-31 and save it as train.csv for faster loading in the future
```{r}
close_data <- data.frame(Date = as.Date(character()))

# Cache the combined close data for faster loading in the future
if (file.exists(paste0("train.csv"))) {
  close_data <- read_csv("train.csv")
} else {
  for (ticker in tickers) {
    ticker <- str_replace_all(ticker, "\\.", "-")
    df <- read_csv(paste0("cache/", ticker, ".csv"), show_col_types = FALSE)
    close_data <- full_join(close_data, df, by = "Date")
    close_data <- close_data[
                             close_data$Date >= as.Date(
                               "2020-01-01"
                             ) & close_data$Date <= as.Date(
                               "2025-12-31"
                             ), ]
  }
  write_csv(close_data, "train.csv")
}
close_data[is.na(close_data)] <- 0
head(close_data)
```

# Combine all the close prices into a single data frame for test set from 2026-01-01 to 2026-03-31 and save it as test.csv for faster loading in the future
```{r}
close_data <- data.frame(Date = as.Date(character()))

# Cache the combined close data for faster loading in the future
if (file.exists(paste0("test.csv"))) {
  close_data <- read_csv("test.csv")
} else {
  for (ticker in tickers) {
    ticker <- str_replace_all(ticker, "\\.", "-")
    df <- read_csv(paste0("cache/", ticker, ".csv"), show_col_types = FALSE)
    close_data <- full_join(close_data, df, by = "Date")
    close_data <- close_data[
                             close_data$Date >= as.Date(
                               "2026-01-01"
                             ) & close_data$Date <= as.Date(
                               "2026-03-31"
                             ), ]
  }
  write_csv(close_data, "test.csv")
}
close_data[is.na(close_data)] <- 0
head(close_data)
```

# Get the weights of the S&P 500 companies from the Slickcharts website
```{r}
weights <- read_html("https://www.slickcharts.com/sp500") |>
  html_table() |>
  _[[1]] |>
  select(Symbol, Weight) |>
  mutate(
    Symbol = str_replace_all(Symbol, "\\.", "-"),
    Weight = as.numeric(str_replace_all(Weight, "%", "")) / 100
  )
head(weights)
```

# Calculate the weighted close price for each company and sum them to get the S&P 500 index value
```{r}
weighted_close_data <- close_data |>
  pivot_longer(-Date, names_to = "Symbol", values_to = "Close") |>
  mutate(Symbol = str_replace_all(Symbol, "\\.Close", "")) |>
  left_join(weights, by = "Symbol") |>
  mutate(Weighted_Close = Close * Weight) |>
  group_by(Date) |>
  summarise(SP500 = sum(Weighted_Close, na.rm = TRUE))
print(weighted_close_data)
```

# Plot the S&P 500 index value over time and compare it with VOO
```{r, fig.height = 4, fig.width = 10}
voo <- loadSymbols(
  Symbols = "VOO",
  from = "2020-01-01",
  to = "2025-12-31",
  auto.assign = FALSE
) |>
  as.data.frame() |>
  rownames_to_column("Date") |>
  mutate(Date = as.Date(Date)) |>
  rename(VOO_Close = voo.Close)

qqq <- loadSymbols(
  Symbols = "QQQ",
  from = "2020-01-01",
  to = "2025-12-31",
  auto.assign = FALSE
) |>
  as.data.frame() |>
  rownames_to_column("Date") |>
  mutate(Date = as.Date(Date)) |>
  rename(QQQ_Close = qqq.Close)

weighted_close_data <- weighted_close_data |>
  mutate(Date = as.Date(Date))

plot_data <- left_join(weighted_close_data, VOO, by = "Date") |>
  left_join(QQQ, by = "Date") |>
  pivot_longer(cols = c(SP500, VOO_Close, QQQ_Close),
               names_to = "Index", values_to = "Value") |>
  group_by(Index) |>
  mutate(Rebased_Value = Value / first(Value)) |>
  ungroup()

ggplot(plot_data, aes(x = Date, y = Rebased_Value, color = Index)) +
  geom_line() +
  labs(title = "S&P 500 Index vs VOO (Rebased to 1)",
       x = "Date",
       y = "Rebased Value") +
  theme_minimal()
```

```{python}
import torch
import torch.nn as nn
import pandas as pd
import numpy as np

# Define the same model architecture
class Net(nn.Module):
    def __init__(self, input_dim, hidden_dim, output_dim):
        super(Net, self).__init__()
        self.fc1 = nn.Linear(input_dim, hidden_dim)
        self.relu = nn.ReLU()
        self.fc2 = nn.Linear(hidden_dim, output_dim)

    def forward(self, x):
        return self.fc2(self.relu(self.fc1(x)))

# Reload the trained model
close_data = pd.read_csv("train.csv", parse_dates=["Date"])
X = close_data.drop(columns=["Date"]).values.astype("float32")
X = np.nan_to_num(X)
X_tensor = torch.tensor(X, dtype=torch.float32)

model = Net(input_dim=X_tensor.shape[1], hidden_dim=32, output_dim=1)
model.load_state_dict(torch.load("test_model.pt"))
model.eval()

# Make predictions
with torch.no_grad():
    preds = model(X_tensor)
print(preds[:5])
```